---
title: "Main functionality"
author: "Dmitriy Demenkov"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

In this vignette you can find basic information about package`s functions usage.

## Load library

To use package you need to load it:

```{r library}
library(rfars)
```

## fars_read example

One of basic function in package, it simply read the specified FARS data file.

```{r fars_read}
library(rfars)
fars_read("accident_2015.csv.bz2")
```

## make_filename example

This function will create correct filename for FARS data file based on year.

```{r make_filename}
make_filename(2015)
```

## fars_read_years example

THis function can read several FARS data files by one use.

```{r fars_read_years}
fars_read_years(2013:2015)
fars_read_years(c("2013", "2015"))
```

## fars_summarize_years example

YOu can use this function in case you want to have short FARS summary for specified years.

```{r fars_summarize_years}
fars_summarize_years(2014:2015)
```

## fars_map_state example

THis function will plot FARS data for specified year and state.

```{r fars_map_state}
fars_map_state(state.num = 34, 2015)
```



